Evolution of Processes in Delivering Reliable Software within the European Scientific Arena

### 2018-09-26 paper-ieee-trans.tex
improved table III, improved reference order, changed fig1 filename
added figure

Project monitoring and reporting mechanisms allowed to assess the risks, efforts and documentation
produced. Development guidelines \cite{datagridguide} were produced, covering the various phases, including
1) packaging, 2) test and validation, and 3) style and naming convention. The specification of quality indicators
\cite{datagridindicators} facilitated the detection of deviations in the collected metric data. Figure 
\ref{fig:efficiency} shows the efficiency performance indicator, measured in production environments as the
number of jobs successfully completed divided by the total number of jobs submitted. As it can be observed,
there is a positive trend of efficiency over the months, with the unique exception of the LCG1 experiment.
\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth, height=50mm]{images/dgeff.png}
\caption{Efficiency \% = Number of jobs successfully completed / Total Number of jobs submitted: results are provided for five experiments involved in the project.}
\label{fig:efficiency}
\end{figure}

@@

\begin{table}[!h]
\renewcommand{\arraystretch}{1.3}
\caption{EMI software quality evolution}
\label{tab:emi}
\centering
\begin{tabular}{lp{1cm}p{1cm}p{1cm}p{1cm}}
\hline
\hline
PQ & Release Products (RP) & N. RP Passed UMD QC & N. RP Passed SR & N. RP Failed UMD QC\\
\hline
\hline
5 & 30 & 27 & 27 & 0\\
6 & 30 & 28 & 26 & 2 \\
7 & 27 & 26& 24& 2\\
8 & 18 & 18 & 18 & 0\\
\hline
\hline
\end{tabular}
\end{table}

@@

>>>>

Project monitoring and reporting mechanisms allowed to assess the risks, efforts and documentation
produced. Development guidelines \cite{datagridguide} were produced, covering the various phases, including
1) packaging, 2) test and validation, and 3) style and naming convention. The specification of quality indicators
\cite{datagridindicators} facilitated the detection of deviations in the collected metric data. Figure
\ref{fig:efficiency} shows the efficiency performance indicator, measured in production environments as the
number of jobs successfully completed divided by the total number of jobs submitted. As it can be observed,
there is a positive trend of efficiency over the months, with the unique exception of the LCG1 experiment.
\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth, height=50mm]{images/datagridEff.png}
\caption{Efficiency \% = Number of jobs successfully completed / Total Number of jobs submitted: results are provided for five experiments involved in the project.}
\label{fig:efficiency}
\end{figure}

@@

\begin{table}[!h]
\renewcommand{\arraystretch}{1.3}
\caption{EMI software quality evolution}
\label{tab:emi}
\centering
\begin{tabular}{lp{1.6cm}p{1.6cm}p{1.3cm}p{1.5cm}}
\hline
\hline
PQ & Release Products (RP) & N. RP Passed UMD QC & N. RP Passed SR & N. RP Failed UMD QC\\
\hline
\hline
5 & 30 & 27 & 27 & 0\\
6 & 30 & 28 & 26 & 2 \\
7 & 27 & 26& 24& 2\\
8 & 18 & 18 & 18 & 0\\
\hline
\hline
\end{tabular}
\end{table}

@@

Figure \ref{fig:ingigobugs}
\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth, height=50mm]{images/indigoBugs.png}
\caption{Number of INDIGO bugs detected during the development and production phases.}
\label{fig:indigobugs}
\end{figure}
